Astronomical Image colorization and up-scaling with generative adversarial networks\\

### 2021-09-15 Presentation/Stage_1/figures/block_diagrams/gan_visualization/gan_visualization.tex

\documentclass[tikz,border=3mm]{standalone}
\usetikzlibrary{chains, calc,fit}
\usepackage{varwidth}
\begin{document}
%\definecolor{offwhite}{RGB}{255, 255, 243}  
%%\pagecolor{offwhite}
\begin{tikzpicture}[box/.style={draw,thick,minimum width=5em,minimum
    height=10em},arj/.style={semithick,-latex}]
  \begin{scope}[start chain=A going right,oc/.style={join=by arj,on chain},
    font=\sffamily,node distance=1.75em]
   \node(color data)[box,minimum height=2.5em, minimum width=7em,anchor=east]at (1.2,1) {$y$ \scriptsize{(Colored Image)}};
   \node(discriminator)[box,minimum height=7em, minimum width=7em,anchor=west] at (4,-2) {\scriptsize{Discriminator}};
   \draw[->] (color data) -| (discriminator);

   \node(generator)[box, minimum height=7em, minimum width=7em] at (0,-2){\scriptsize{Generator}};
   \draw[<-] (generator.west) -- node[above]{\tiny{$x$(input image)}} ++(-5em,0em);

   \node(generator func)[box, minimum height = 2em, minimum width = 1em] at (2.5,-2){\scriptsize{$G(x)$}};
   \draw[<-] (generator func) -- (generator);
   \draw[->] (generator func) -- (discriminator);

   \node(discriminator func)[box, minimum height = 2em, minimum width = 1em] at (8, -2){\scriptsize{$D\big(G(x),y\big)$}};

>>>>

\documentclass[tikz,border=3mm]{standalone}
\usetikzlibrary{chains, calc,fit}
\usepackage{varwidth}
\begin{document}
%\definecolor{offwhite}{RGB}{255, 255, 243}  
%\pagecolor{offwhite}
\begin{tikzpicture}[box/.style={draw,thick,minimum width=5em,minimum
    height=10em},arj/.style={semithick,-latex}]
  \begin{scope}[start chain=A going right,oc/.style={join=by arj,on chain},
    font=\sffamily,node distance=1.75em]

   \node(color data)[outer sep=0pt,inner sep=0pt,label=Ground Truth] at (1.2,1) {\includegraphics[width=2cm]{figures/ground_truth.jpg}};
   \node(discriminator)[box,minimum height=7em, minimum width=7em,anchor=west] at (4,-2) {\scriptsize{Discriminator}}; 
   \draw[->] (color data) -| (discriminator);

   \node(generator)[box, minimum height=7em, minimum width=7em] at (-2,-2){\scriptsize{Generator}};
   \node(input image)[outer sep=0pt,inner sep=0pt,label=Grayscale Image] at (-5.5,-2) {\includegraphics[width=2cm]{figures/input_grayscale.jpg}};
   \draw[->] (input image) -- (generator);

   \node(generator func)[outer sep=0pt,inner sep=0pt,label=Generated Image] at (1.2,-2){\includegraphics[width=2cm]{figures/generated_output.jpg}};
   \draw[<-] (generator func) -- (generator);
   \draw[->] (generator func) -- (discriminator);

   \node(discriminator func)[box, minimum height = 2em, minimum width = 1em] at (8, -2){\textit{\scriptsize{p = 0.82}}};

### 2021-09-15 Research Paper/paper.tex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
\usepackage[authoryear]{natbib}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{hyperref} 
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{multirow}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Astronomical Image colorization and up-scaling with generative adversarial networks\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

Table \ref{color_results} shows that the RGB color space performs poorly on the task of colorization. In terms of the L1 distance, the best performance is achieved on the ResNet18 U-net with pre-trained weights. This goes to prove the unreliability of distance metrics in model performance evaluation. The model, although quantitatively, performs better than the fine-tuned model but in reality, fails to produce images that might be visually appealing. The L2 distance metric shows how the fine-tuned model might, in reality, be fitting slightly better over the data to predict correct color combination as its output. We still consider the results from the fine tuned model to be better than the other performing models and further investigate the per-channel predictions by the model.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
\usepackage[authoryear]{natbib}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{hyperref} 
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}} 
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{multirow}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Astronomical Image colorization and up-scaling with generative adversarial networks\\
}

@@

Figure \ref{color_results} shows that the RGB color space performs poorly on the task of colorization. In terms of the L1 distance, the best performance is achieved on the ResNet18 U-net with pre-trained weights. This goes to prove the unreliability of distance metrics in model performance evaluation. The model, although quantitatively, performs better than the fine-tuned model but in reality, fails to produce images that might be visually appealing. The L2 distance metric shows how the fine-tuned model might, in reality, be fitting slightly better over the data to predict correct color combination as its output. We still consider the results from the fine tuned model to be better than the other performing models and further investigate the per-channel predictions by the model.
